---
title: "TOPC Cohort 3 Analysis"
subtitle: "Post-test"
author: "Elham Ali"
date: Dec 11, 2023
format:
  html:
    toc: true
    code-fold: true
    code-summary: "Show the code"
editor: visual
cache: true
---

Graphs for post-test survey analysis for city governments.

## Install necessary packages

```{r}
#| label: packages-installation
#| message: false

# Set a CRAN mirror
options(repos = c(CRAN = "https://cloud.r-project.org"))

# Install necessary packages
# install.packages("magrittr")
# install.packages("dplyr")
# install.packages("ggplot2")
# install.packages("knitr")
# install.packages("kableExtra")
# install.packages("survey")
# install.packages("plotly")

# Load the packages
library(magrittr)
library(dplyr)
library(plotly)
library(ggplot2)
library(knitr)
library(kableExtra)
library(survey)
```

## Survey design weights

<div>

```{r}
#| label: design-weights
#| message: false

# Read the data from the CSV file
cohort3FinalGov3 <- read.csv("~/Documents/R_Projects/TOPC-impact-evaluation-dashboard/Cohort_3/cohort3FinalGov3.csv") 

# Define population and sample sizes
population_counts <- c(Akron = 8, Detroit = 9, Macon = 10, Miami = 13)
sample_counts <- c(Akron = 4, Detroit = 2, Macon = 4, Miami = 3)

# Total population and sample size
total_population <- sum(population_counts)
total_sample <- sum(sample_counts)

# Calculate the weights
weights <- (population_counts / total_population) / (sample_counts / total_sample)

# Print the calculated weights
print(weights)
```

</div>

```{r}
#| label: survey-design-definition
#| message: false

# Convert Likert scale questions to numeric
likert_questions <- c("q4", "q5", "q6", "q7", "q9", "q10", "q11", "q12", "q13", "q14", "q15", "q16", "q17", "q20", "q21")
for (question in likert_questions) {
    cohort3FinalGov3[[question]] <- as.numeric(as.character(cohort3FinalGov3[[question]]))
}

# Map between city names 
city_map <- list(
  "Miami-Dade County, FL" = "Miami",
  "Akron, OH" = "Akron",
  "Detroit, MI" = "Detroit",
  "Macon-Bibb County, GA" = "Macon"
)

# Update dataframe to use the mapped names
cohort3FinalGov3$city_mapped <- unlist(lapply(cohort3FinalGov3$q3, function(x) city_map[[x]]))

# Assign weights using the mapped city names
cohort3FinalGov3$weights <- weights[cohort3FinalGov3$city_mapped]

# Define the survey design
design <- svydesign(ids = ~1, 
                    strata = ~city_mapped, 
                    weights = ~weights, 
                    data = cohort3FinalGov3)
```

Given this in the data:

| City Teams | Population Count | Sample Count |
|------------|------------------|--------------|
| Akron      | 8                | 4            |
| Detroit    | 9                | 2            |
| Macon      | 10               | 4            |
| Miami      | 13               | 3            |
| Total      | 40               | 13           |

: **Table 1.** Count of population and sample participants in city governments in the TOPC program in Cohort 3

The formula I used to align proportions of population to proportions of sample)

$\text{Weight of strata} = \frac{\frac{\text{Strata Population}}{\text{Total Population}}}{\frac{\text{Strata Sample}}{\text{Total Sample}}}$

$\text{Weight for Akron} = \frac{\frac{8}{40}}{\frac{4}{14}} = \frac{0.2}{0.2857} \approx 0.700$

$\text{Weight for Detroit} = \frac{\frac{9}{40}}{\frac{2}{14}} = \frac{0.225}{0.1429} \approx 1.575$

$\text{Weight for Macon} = \frac{\frac{10}{40}}{\frac{4}{14}} = \frac{0.25}{0.2857} \approx 0.875$

$\text{Weight for Miami} = \frac{\frac{13}{40}}{\frac{3}{14}} = \frac{0.325}{0.2143} \approx 1.517$

## Descriptive data analysis

#### Per Question

For Q4

Please note that the absence of confidence intervals and standard errors for the median in the strata of Akron, Detroit, and Miami could be due to the **`svyquantile`** function not being able to compute these values with the available data. This is typically due to small sample sizes or other limitations in the data. The confidence interval for Macon, being precise, might suggest limited responses or a lack of variation in the responses for that stratum.

-   **Akron**

    -   **Median**: The median response is 3, which means the central tendency of the responses is "Agree".

    -   **Standard Deviation**: The standard deviation is approximately 0.50. This value indicates moderate variability in the responses, suggesting that while "Agree" is the median response, there is some dispersion around this central value.

-   **Detroit**

    -   **Median**: The median response is 3, similar to Akron, indicating "Agree" as the central response.

    -   **Standard Deviation**: The standard deviation is approximately 0.71, which suggests a slightly higher variability in responses compared to Akron.

-   **Macon**

    -   **Median**: The median response is 3 with a confidence interval from 3 to 3, which indicates a very consistent agreement among the participants, as the central response is "Agree" with little to no variability.

    -   **Standard Deviation**: The standard deviation is 0, which means there is no variability among the responses, and all respondents provided the same answer.

-   **Miami**

    -   **Median**: The median response is also 3, indicating "Agree" as the central response.

    -   **Standard Deviation**: The standard deviation is approximately 0.58, suggesting a moderate level of variability, similar to Akron.

```{r}
#| label: central-tendancy-per-question
#| message: false

# Define the strata
strata <- c("Akron", "Detroit", "Macon", "Miami")

# Initialize a data frame to store the results for question q4
results_df <- data.frame(
    Stratum = character(),
    Median = numeric(),
    StandardDeviation = numeric(),
    stringsAsFactors = FALSE
)

# Calculate stats for question q4 across each stratum
for (stratum in strata) {
    # Create stratum-specific design
    stratum_design <- subset(design, city_mapped == stratum)
    
    # Calculate weighted median for q4
    median_val <- svyquantile(~q4, stratum_design, 0.5, na.rm = TRUE)
    
    # Calculate weighted standard deviation for q4
    sd_val <- sqrt(svyvar(~q4, stratum_design, na.rm = TRUE))
    
    # Extract the median and standard deviation values
    median_q4 <- median_val[1]  # Extracting the median value for q4
    sd_q4 <- sd_val[1]  # Extracting the SD value for q4
    
    # Append the results to the data frame
    results_df <- rbind(results_df, data.frame(
        Stratum = stratum,
        Median = median_q4,
        StandardDeviation = sd_q4
    ))
}

# Print the results for q4
print(results_df)
```

#### Per City Government Team

-   1 = Strongly disagree

-   2 = Disagree

-   3 = Agree

-   4 = Strongly agree

```{r}
#| label: central-tendancy-per-stratum-across-all-questions
#| message: false


```

## Participant Background

**Q3. Which city/county are you representing?**

```{r}
#| label: q3
#| message: false

# Single-variable frequency plot
q3_frequency <- svytable(~q3, design = design)

ggplot(as.data.frame(q3_frequency), aes(x = q3, y = Freq)) +
  geom_bar(stat = "identity", fill = "#041e42", width = 0.7) +
  coord_flip() +
  labs(title = "All city governments participated in the survey with the 
highest number of respondents from Miami-Dade and 
Macon-Bibb Counties.",
       subtitle = paste("Total number of survey respondents per city team (n =", total_sample, ")"),
       x = "",
       y = "Number of Responses") +
  theme_minimal() + 
  theme(legend.position = "bottom",
        legend.box = "vertical",
        legend.box.margin = margin(0, 0, 0, 0),
        legend.title = element_blank(),
        panel.grid.major.y = element_blank(),
        panel.grid.minor.y = element_blank(),
        plot.title = element_text(face = "bold"),
        plot.caption = element_text(hjust = 0)) +
  guides(fill = guide_legend(nrow = 1, byrow = TRUE))
```

**Q25. Which title best describes your role and level of seniority at work?**

```{r}
#| label: q25
#| message: false

# Single-variable frequency plot
q25_frequency <- svytable(~q25, design = design)

ggplot(as.data.frame(q25_frequency), aes(x = q25, y = Freq)) +
  geom_bar(stat = "identity", fill = "#041e42", width = 0.7) +
  coord_flip() +
  labs(title = "Majority of respondents are senior officials or 
managers.",
       subtitle = paste("Total number of survey respondents (n =", total_sample, ")"),
       x = "",
       y = "Number of Responses") +
  theme_minimal() + 
  theme(legend.position = "bottom",
        legend.box = "vertical",
        legend.box.margin = margin(0, 0, 0, 0),
        legend.title = element_blank(),
        panel.grid.major.y = element_blank(),
        panel.grid.minor.y = element_blank(),
        plot.title = element_text(face = "bold"),
        plot.caption = element_text(hjust = 0)) +
  guides(fill = guide_legend(nrow = 1, byrow = TRUE))

# # Cross-tabulation with cities
# colors <- c("#041e42", "#6eaddc", "#da291c", "#1B786E", "#e69138", "#5b9bd5", "#a4c739")
# 
# q25_cross_tab_city <- svytable(~q25 + city_mapped, design = design)
# 
# ggplot(as.data.frame(q25_cross_tab_city), aes(x = city_mapped, y = Freq, fill = q25)) +
#   geom_bar(stat = "identity", position = "stack") +
#   coord_flip() +
#   scale_fill_manual(values = colors) +  # Assign the colors to the categories
#   labs(title = "Distribution of Q25 Responses Across Cities",
#        subtitle = paste("Responses for Q25 (n =", total_sample, ")"),
#        x = "",
#        y = "Number of Responses",
#        caption = "Source: TOPC Cohort 3 Survey (2023)") +
#   theme_minimal() +
#   theme(legend.position = "bottom",
#         legend.box = "vertical",
#         legend.box.margin = margin(0, 0, 0, 0),
#         legend.title = element_blank(),
#         panel.grid.major.y = element_blank(),
#         panel.grid.minor.y = element_blank(),
#         plot.title = element_text(face = "bold"),
#         plot.caption = element_text(hjust = 0)) +
#   guides(fill = guide_legend(nrow = 1, byrow = TRUE))
```

**Q27. How many years have you worked at your respective City or County?**

```{r}
#| label: q27
#| message: false

# Single-variable frequency plot
q27_frequency <- svytable(~q27, design = design)

ggplot(as.data.frame(q27_frequency), aes(x = q27, y = Freq)) +
  geom_bar(stat = "identity", fill = "#041e42", width = 0.7) +
  coord_flip() +
  labs(title = "Majority are new to working in their city or county governments.",
       subtitle = paste("Total number of survey respondents (n =", total_sample, ")"),
       x = "",
       y = "Number of Responses") +
  theme_minimal() + 
  theme(legend.position = "bottom",
        legend.box = "vertical",
        legend.box.margin = margin(0, 0, 0, 0),
        legend.title = element_blank(),
        panel.grid.major.y = element_blank(),
        panel.grid.minor.y = element_blank(),
        plot.title = element_text(face = "bold"),
        plot.caption = element_text(hjust = 0)) +
  guides(fill = guide_legend(nrow = 1, byrow = TRUE))

# Cross-tabulation with cities
q27_cross_tab_city <- svytable(~q27 + city_mapped, design = design)

ggplot(as.data.frame(q27_cross_tab_city), aes(x = city_mapped, y = Freq, fill = q27)) +
  geom_bar(stat = "identity", position = "stack") +
  coord_flip() +
  scale_fill_manual(values = c("#041e42","#6eaddc","#da291c","#1B786E"),
                    limits = c("0-2 years", "3-5 years", "6-9 years", "10+ years")) + 
  labs(title = "Majority are new to working to city and county governments, 
especially in Macon and Detroit.",
       subtitle = paste("Years of Experience: Range from 0 to 10+ years (n =", total_sample, ")"),
       x = "",
       y = "Number of Responses",
       caption = "Source: TOPC Cohort 3 Survey (2023)") +
  theme_minimal() +
  theme(legend.position = "bottom",
        legend.box = "vertical",
        legend.box.margin = margin(0, 0, 0, 0),
        legend.title = element_blank(),
        panel.grid.major.y = element_blank(),
        panel.grid.minor.y = element_blank(),
        plot.title = element_text(face = "bold"),
        plot.caption = element_text(hjust = 0)) +
  guides(fill = guide_legend(nrow = 1, byrow = TRUE))
```

**Q28. Please describe your racial/ethnic identity. Select all that apply.**

```{r}
#| label: q28
#| message: false

# Single-variable frequency plot
q28_frequency <- svytable(~q28, design = design)

ggplot(as.data.frame(q28_frequency), aes(x = q28, y = Freq)) +
  geom_bar(stat = "identity", fill = "#041e42", width = 0.7) +
  coord_flip() +
  labs(title = "Majority are new to working in their city or county governments.",
       subtitle = paste("Total number of survey respondents (n =", total_sample, ")"),
       x = "",
       y = "Number of Responses") +
  theme_minimal() + 
  theme(legend.position = "bottom",
        legend.box = "vertical",
        legend.box.margin = margin(0, 0, 0, 0),
        legend.title = element_blank(),
        panel.grid.major.y = element_blank(),
        panel.grid.minor.y = element_blank(),
        plot.title = element_text(face = "bold"),
        plot.caption = element_text(hjust = 0)) +
  guides(fill = guide_legend(nrow = 1, byrow = TRUE))
```

**Q29. Which gender do you most closely identify with (or self-describe in 'other')?**

```{r}
#| label: q29
#| message: false

# Single-variable frequency plot
q29_frequency <- svytable(~q29, design = design)

ggplot(as.data.frame(q29_frequency), aes(x = q29, y = Freq)) +
  geom_bar(stat = "identity", fill = "#041e42", width = 0.7) +
  coord_flip() +
  labs(title = "More than half of respondents identify as male.",
       subtitle = paste("Total number of survey respondents (n =", total_sample, ")"),
       x = "",
       y = "Number of Responses") +
  theme_minimal() + 
  theme(legend.position = "bottom",
        legend.box = "vertical",
        legend.box.margin = margin(0, 0, 0, 0),
        legend.title = element_blank(),
        panel.grid.major.y = element_blank(),
        panel.grid.minor.y = element_blank(),
        plot.title = element_text(face = "bold"),
        plot.caption = element_text(hjust = 0)) +
  guides(fill = guide_legend(nrow = 1, byrow = TRUE))
```

```{r}
#| label: weighted-vs-unweighted-counts
#| message: false
# Compare weighted vs. unweighted counts:
# # Unweighted count
# unweighted_counts <- table(cohort3FinalGov3$q3)
# 
# # Weighted count
# weighted_counts <- svytable(~q3, design = design)
# 
# # Compare
# print(unweighted_counts)
# print(weighted_counts)
```

```{r}
#| label: weighted-summary-statistics
#| message: false

# Review weighted summary statistics:
# # Weighted mean
# weighted_mean <- svymean(~q3, design = design)
# 
# # Weighted total
# weighted_total <- svytotal(~q3, design = design)
# 
# # Display the results
# print(weighted_mean)
# print(weighted_total)
```

## Goal 1: Participant Awareness and Knowledge

**Q4. I learned new skills in community research practices, such as leading interviews and conducting surveys, during this program.**

```{r}
#| label: q4-descriptive stat plot
#| message: false

# Single-variable frequency plot
q4_frequency <- svytable(~q4, design = design)

ggplot(as.data.frame(q4_frequency), aes(x = q4, y = Freq)) +
  geom_bar(stat = "identity", fill = "#041e42", width = 0.7) +
  coord_flip() +
  labs(title = "All respondents agree they learned new skills in community 
research practices.",
       subtitle = paste("Rating Scale: 4 - Strongly Agree to 1 - Strongly Disagree (n =", total_sample, ")"),
       x = "",
       y = "Number of Responses") +
  theme_minimal() + 
  theme(panel.grid.major.y = element_blank(),
        panel.grid.minor.y = element_blank(),
        plot.title = element_text(face = "bold"))

# Cross-tabulation with cities
q4_cross_tab_city <- svytable(~q4 + city_mapped, design = design)

ggplot(as.data.frame(q4_cross_tab_city), aes(x = city_mapped, y = Freq, fill = q4)) +
  geom_bar(stat = "identity", position = "stack") +
  coord_flip() +
  scale_fill_manual(values = c("#041e42","#6eaddc","#da291c","#1B786E"),
                    limits = c("Strongly agree", "Agree", "Disagree", "Strongly disagree")) + 
  labs(title = "Majority agree that they learned community research skills, and
some strongly agreeing, particularly in Miami and Detroit.",
       subtitle = paste("Rating Scale: 4 - Strongly Agree to 1 - Strongly Disagree (n =", total_sample, ")"),
       x = "",
       y = "Number of Responses",
       caption = "Source: TOPC Cohort 3 Survey (2023)") +
  theme_minimal() +
  theme(legend.position = "bottom",
        legend.box = "vertical",
        legend.box.margin = margin(0, 0, 0, 0),
        legend.title = element_blank(),
        panel.grid.major.y = element_blank(),
        panel.grid.minor.y = element_blank(),
        plot.title = element_text(face = "bold"),
        plot.caption = element_text(hjust = 0)) +
  guides(fill = guide_legend(nrow = 1, byrow = TRUE))

# # Descriptive statistics
# # Convert svytable objects to data frames
# q4_frequency_df <- as.data.frame(q4_frequency)
# q4_cross_tab_city_df <- as.data.frame(q4_cross_tab_city)
# 
# # Calculate descriptive statistics
# # For q4_frequency
# q4_freq_stats_weighted <- q4_frequency_df %>%
#   summarise(WeightedMean = sum(WeightedFreq) / sum(Freq),
#             WeightedSD = sd(WeightedValue, weights = Freq))
# 
# # For q4_cross_tab_city
# q4_cross_tab_stats_weighted <- q4_cross_tab_city_df %>%
#   group_by(city_mapped) %>%
#   summarise(WeightedMean = sum(WeightedFreq) / sum(Freq),
#             WeightedSD = sd(WeightedValue, weights = Freq))
# 
# # Print results
# print(q4_freq_stats_weighted)
# print(q4_cross_tab_stats_weighted)
```

```{r}
#| label: q4-likert-scale-weights
#| message: false

# # Assign weights to responses
# weight_mapping <- c("Strongly agree" = 4, "Agree" = 3, "Disagree" = 2, "Strongly disagree" = 1)
# 
# # Apply weights to q4_frequency_df
# q4_frequency_df$WeightedValue <- weight_mapping[q4_frequency_df$q4]
# q4_frequency_df$WeightedFreq <- q4_frequency_df$Freq * q4_frequency_df$WeightedValue
# 
# # Apply weights to q4_cross_tab_city_df
# q4_cross_tab_city_df$WeightedValue <- weight_mapping[q4_cross_tab_city_df$q4]
# q4_cross_tab_city_df$WeightedFreq <- q4_cross_tab_city_df$Freq * q4_cross_tab_city_df$WeightedValue
```

**Q5. I learned skills to promote equity and foster inclusive spaces in my work.**

```{r}
#| label: q5
#| message: false

# Single-variable frequency plot
q5_frequency <- svytable(~q5, design = design)

ggplot(as.data.frame(q5_frequency), aes(x = q5, y = Freq)) +
  geom_bar(stat = "identity", fill = "#041e42", width = 0.7) +
  coord_flip() +
  labs(title = "All respondents agree they learned new skills to promote
equity and inclusion in their work.",
       subtitle = paste("Rating Scale: 4 - Strongly Agree to 1 - Strongly Disagree (n =", total_sample, ")"),
       x = "",
       y = "Number of Responses") +
  theme_minimal() + 
  theme(panel.grid.major.y = element_blank(),
        panel.grid.minor.y = element_blank(),
        plot.title = element_text(face = "bold"))

# Cross-tabulation with cities
q5_cross_tab_city <- svytable(~q5 + city_mapped, design = design)

ggplot(as.data.frame(q5_cross_tab_city), aes(x = city_mapped, y = Freq, fill = q5)) +
  geom_bar(stat = "identity", position = "stack") +
  coord_flip() +
  scale_fill_manual(values = c("#041e42","#6eaddc","#da291c","#1B786E"),
                    limits = c("Strongly agree", "Agree", "Disagree", "Strongly disagree")) + 
  labs(title = "Majority agree that they learned equity and inclusion skills, and
some strongly agreeing, particularly in Miami and Macon.",
       subtitle = paste("Rating Scale: 4 - Strongly Agree to 1 - Strongly Disagree (n =", total_sample, ")"),
       x = "",
       y = "Number of Responses",
       caption = "Source: TOPC Cohort 3 Survey (2023)") +
  theme_minimal() +
  theme(legend.position = "bottom",
        legend.box = "vertical",
        legend.box.margin = margin(0, 0, 0, 0),
        legend.title = element_blank(),
        panel.grid.major.y = element_blank(),
        panel.grid.minor.y = element_blank(),
        plot.title = element_text(face = "bold"),
        plot.caption = element_text(hjust = 0)) +
  guides(fill = guide_legend(nrow = 1, byrow = TRUE))
```

**Q6. I learned new skills in applying user testing feedback to shape the development of our solution.**

```{r}
#| label: q6
#| message: false

# Single-variable frequency plot
q6_frequency <- svytable(~q6, design = design)

ggplot(as.data.frame(q6_frequency), aes(x = q6, y = Freq)) +
  geom_bar(stat = "identity", fill = "#041e42", width = 0.7) +
  coord_flip() +
  labs(title = "All respondents agree they learned new skills to apply user 
testing feedback in their solution development.",
       subtitle = paste("Rating Scale: 4 - Strongly Agree to 1 - Strongly Disagree (n =", total_sample, ")"),
       x = "",
       y = "Number of Responses") +
  theme_minimal() + 
  theme(panel.grid.major.y = element_blank(),
        panel.grid.minor.y = element_blank(),
        plot.title = element_text(face = "bold"))

# Cross-tabulation with cities
q6_cross_tab_city <- svytable(~q6 + city_mapped, design = design)

ggplot(as.data.frame(q6_cross_tab_city), aes(x = city_mapped, y = Freq, fill = q6)) +
  geom_bar(stat = "identity", position = "stack") +
  coord_flip() +
  scale_fill_manual(values = c("#041e42","#6eaddc","#da291c","#1B786E"),
                    limits = c("Strongly agree", "Agree", "Disagree", "Strongly disagree")) + 
  labs(title = "Majority agree that they learned user testing skills to develop their 
solutions, with Miami strongly agreeing the most.",
       subtitle = paste("Rating Scale: 4 - Strongly Agree to 1 - Strongly Disagree (n =", total_sample, ")"),
       x = "",
       y = "Number of Responses",
       caption = "Source: TOPC Cohort 3 Survey (2023)") +
  theme_minimal() +
  theme(legend.position = "bottom",
        legend.box = "vertical",
        legend.box.margin = margin(0, 0, 0, 0),
        legend.title = element_blank(),
        panel.grid.major.y = element_blank(),
        panel.grid.minor.y = element_blank(),
        plot.title = element_text(face = "bold"),
        plot.caption = element_text(hjust = 0)) +
  guides(fill = guide_legend(nrow = 1, byrow = TRUE))
```

**Q15. I learned new skills in collaborating with a community organization to research a problem and co-design a solution.**

```{r}
#| label: q15
#| message: false

# Single-variable frequency plot
q15_frequency <- svytable(~q15, design = design)

ggplot(as.data.frame(q15_frequency), aes(x = q15, y = Freq)) +
  geom_bar(stat = "identity", fill = "#041e42", width = 0.7) +
  coord_flip() +
  labs(title = "All respondents agree they learned new skills to collaborate 
with a community organization from problem discovery to 
solution co-design.",
       subtitle = paste("Rating Scale: 4 - Strongly Agree to 1 - Strongly Disagree (n =", total_sample, ")"),
       x = "",
       y = "Number of Responses") +
  theme_minimal() + 
  theme(panel.grid.major.y = element_blank(),
        panel.grid.minor.y = element_blank(),
        plot.title = element_text(face = "bold"))

# Cross-tabulation with cities
q15_cross_tab_city <- svytable(~q15 + city_mapped, design = design)

ggplot(as.data.frame(q15_cross_tab_city), aes(x = city_mapped, y = Freq, fill = q15)) +
  geom_bar(stat = "identity", position = "stack") +
  coord_flip() +
  scale_fill_manual(values = c("#041e42","#6eaddc","#da291c","#1B786E"),
                    limits = c("Strongly agree", "Agree", "Disagree", "Strongly disagree")) + 
  labs(title = "Majority agree that they learned skills to collaborate with a community 
organization, with Akron strongly agreeing the most.",
       subtitle = paste("Rating Scale: 4 - Strongly Agree to 1 - Strongly Disagree (n =", total_sample, ")"),
       x = "",
       y = "Number of Responses",
       caption = "Source: TOPC Cohort 3 Survey (2023)") +
  theme_minimal() +
  theme(legend.position = "bottom",
        legend.box = "vertical",
        legend.box.margin = margin(0, 0, 0, 0),
        legend.title = element_blank(),
        panel.grid.major.y = element_blank(),
        panel.grid.minor.y = element_blank(),
        plot.title = element_text(face = "bold"),
        plot.caption = element_text(hjust = 0)) +
  guides(fill = guide_legend(nrow = 1, byrow = TRUE))
```

**Q16. I learned new skills in building consensus and aligning on long-term plans with internal stakeholders.**

```{r}
#| label: q16
#| message: false

# Single-variable frequency plot
q16_frequency <- svytable(~q16, design = design)

ggplot(as.data.frame(q16_frequency), aes(x = q16, y = Freq)) +
  geom_bar(stat = "identity", fill = "#041e42", width = 0.7) +
  coord_flip() +
  labs(title = "All respondents agree they learned news skills to build 
consensus and align on long-term plans with internal stakeholders.",
       subtitle = paste("Rating Scale: 4 - Strongly Agree to 1 - Strongly Disagree (n =", total_sample, ")"),
       x = "",
       y = "Number of Responses") +
  theme_minimal() + 
  theme(panel.grid.major.y = element_blank(),
        panel.grid.minor.y = element_blank(),
        plot.title = element_text(face = "bold"))

# Cross-tabulation with cities
q16_cross_tab_city <- svytable(~q16 + city_mapped, design = design)

ggplot(as.data.frame(q16_cross_tab_city), aes(x = city_mapped, y = Freq, fill = q16)) +
  geom_bar(stat = "identity", position = "stack") +
  coord_flip() +
  scale_fill_manual(values = c("#041e42","#6eaddc","#da291c","#1B786E"),
                    limits = c("Strongly agree", "Agree", "Disagree", "Strongly disagree")) + 
  labs(title = "Majority agree that they learned skills to build build internal 
consensus, with Detroit and Akron agreeing the most.",
       subtitle = paste("Rating Scale: 4 - Strongly Agree to 1 - Strongly Disagree (n =", total_sample, ")"),
       x = "",
       y = "Number of Responses",
       caption = "Source: TOPC Cohort 3 Survey (2023)") +
  theme_minimal() +
  theme(legend.position = "bottom",
        legend.box = "vertical",
        legend.box.margin = margin(0, 0, 0, 0),
        legend.title = element_blank(),
        panel.grid.major.y = element_blank(),
        panel.grid.minor.y = element_blank(),
        plot.title = element_text(face = "bold"),
        plot.caption = element_text(hjust = 0)) +
  guides(fill = guide_legend(nrow = 1, byrow = TRUE))
```

**Q9. I learned different strategies to brainstorm many ideas based on the insights taken from the community research.**

```{r}
#| label: q9
#| message: false

# Single-variable frequency plot
q9_frequency <- svytable(~q9, design = design)

ggplot(as.data.frame(q9_frequency), aes(x = q9, y = Freq)) +
  geom_bar(stat = "identity", fill = "#041e42", width = 0.7) +
  coord_flip() +
  labs(title = "All respondents agree they learned different strategies to 
brainstorm ideas based on community research insights.",
       subtitle = paste("Rating Scale: 4 - Strongly Agree to 1 - Strongly Disagree (n =", total_sample, ")"),
       x = "",
       y = "Number of Responses") +
  theme_minimal() + 
  theme(panel.grid.major.y = element_blank(),
        panel.grid.minor.y = element_blank(),
        plot.title = element_text(face = "bold"))

# Cross-tabulation with cities
q9_cross_tab_city <- svytable(~q9 + city_mapped, design = design)

ggplot(as.data.frame(q9_cross_tab_city), aes(x = city_mapped, y = Freq, fill = q9)) +
  geom_bar(stat = "identity", position = "stack") +
  coord_flip() +
  scale_fill_manual(values = c("#041e42","#6eaddc","#da291c","#1B786E"),
                    limits = c("Strongly agree", "Agree", "Disagree", "Strongly disagree")) + 
  labs(title = "Majority agree that they learned different strategories to brainstorm 
ideas using community research, but some disagree in Miami and Macon.",
       subtitle = paste("Rating Scale: 4 - Strongly Agree to 1 - Strongly Disagree (n =", total_sample, ")"),
       x = "",
       y = "Number of Responses",
       caption = "Source: TOPC Cohort 3 Survey (2023)") +
  theme_minimal() +
  theme(legend.position = "bottom",
        legend.box = "vertical",
        legend.box.margin = margin(0, 0, 0, 0),
        legend.title = element_blank(),
        panel.grid.major.y = element_blank(),
        panel.grid.minor.y = element_blank(),
        plot.title = element_text(face = "bold"),
        plot.caption = element_text(hjust = 0)) +
  guides(fill = guide_legend(nrow = 1, byrow = TRUE))
```

**Q10. I learned new skills in outlining and prioritizing requirements for the development of a digital product.**

```{r}
#| label: q10
#| message: false

# Single-variable frequency plot
q10_frequency <- svytable(~q10, design = design)

ggplot(as.data.frame(q10_frequency), aes(x = q10, y = Freq)) +
  geom_bar(stat = "identity", fill = "#041e42", width = 0.7) +
  coord_flip() +
  labs(title = "All respondents agree they learned new skills to prioritize 
requirements to develop a digital product.",
       subtitle = paste("Rating Scale: 4 - Strongly Agree to 1 - Strongly Disagree (n =", total_sample, ")"),
       x = "",
       y = "Number of Responses") +
  theme_minimal() + 
  theme(panel.grid.major.y = element_blank(),
        panel.grid.minor.y = element_blank(),
        plot.title = element_text(face = "bold"))

# Cross-tabulation with cities
q10_cross_tab_city <- svytable(~q10 + city_mapped, design = design)

ggplot(as.data.frame(q10_cross_tab_city), aes(x = city_mapped, y = Freq, fill = q10)) +
  geom_bar(stat = "identity", position = "stack") +
  coord_flip() +
  scale_fill_manual(values = c("#041e42","#6eaddc","#da291c","#1B786E"),
                    limits = c("Strongly agree", "Agree", "Disagree", "Strongly disagree")) + 
  labs(title = "Majority agree that they learned new skills to prioritize requirements 
to develop a digital product, with Miami and Detroit strongly agreeing
the most.",
       subtitle = paste("Rating Scale: 4 - Strongly Agree to 1 - Strongly Disagree (n =", total_sample, ")"),
       x = "",
       y = "Number of Responses",
       caption = "Source: TOPC Cohort 3 Survey (2023)") +
  theme_minimal() +
  theme(legend.position = "bottom",
        legend.box = "vertical",
        legend.box.margin = margin(0, 0, 0, 0),
        legend.title = element_blank(),
        panel.grid.major.y = element_blank(),
        panel.grid.minor.y = element_blank(),
        plot.title = element_text(face = "bold"),
        plot.caption = element_text(hjust = 0)) +
  guides(fill = guide_legend(nrow = 1, byrow = TRUE))
```

**Q11. I learned new skills in identifying and evaluating data to support the digital solution.**

```{r}
#| label: q11
#| message: false

# Single-variable frequency plot
q11_frequency <- svytable(~q11, design = design)

ggplot(as.data.frame(q11_frequency), aes(x = q11, y = Freq)) +
  geom_bar(stat = "identity", fill = "#041e42", width = 0.7) +
  coord_flip() +
  labs(title = "All respondents agree they learned new skills to identify and 
evaluate data.",
       subtitle = paste("Rating Scale: 4 - Strongly Agree to 1 - Strongly Disagree (n =", total_sample, ")"),
       x = "",
       y = "Number of Responses") +
  theme_minimal() + 
  theme(panel.grid.major.y = element_blank(),
        panel.grid.minor.y = element_blank(),
        plot.title = element_text(face = "bold"))

# Cross-tabulation with cities
q11_cross_tab_city <- svytable(~q11 + city_mapped, design = design)

ggplot(as.data.frame(q11_cross_tab_city), aes(x = city_mapped, y = Freq, fill = q11)) +
  geom_bar(stat = "identity", position = "stack") +
  coord_flip() +
  scale_fill_manual(values = c("#041e42","#6eaddc","#da291c","#1B786E"),
                    limits = c("Strongly agree", "Agree", "Disagree", "Strongly disagree")) + 
  labs(title = "Majority agree that they learned new skills to identify and evaluate 
data, with Miami and Detroit strongly agreeing the most.",
       subtitle = paste("Rating Scale: 4 - Strongly Agree to 1 - Strongly Disagree (n =", total_sample, ")"),
       x = "",
       y = "Number of Responses",
       caption = "Source: TOPC Cohort 3 Survey (2023)") +
  theme_minimal() +
  theme(legend.position = "bottom",
        legend.box = "vertical",
        legend.box.margin = margin(0, 0, 0, 0),
        legend.title = element_blank(),
        panel.grid.major.y = element_blank(),
        panel.grid.minor.y = element_blank(),
        plot.title = element_text(face = "bold"),
        plot.caption = element_text(hjust = 0)) +
  guides(fill = guide_legend(nrow = 1, byrow = TRUE))
```

**Q12. I learned new skills for managing the development of a digital product.**

```{r}
#| label: q12
#| message: false

# Single-variable frequency plot
q12_frequency <- svytable(~q12, design = design)

ggplot(as.data.frame(q12_frequency), aes(x = q12, y = Freq)) +
  geom_bar(stat = "identity", fill = "#041e42", width = 0.7) +
  coord_flip() +
  labs(title = "Most respondents agree they learned new skills to manage
developing a digital product.",
       subtitle = paste("Rating Scale: 4 - Strongly Agree to 1 - Strongly Disagree (n =", total_sample, ")"),
       x = "",
       y = "Number of Responses") +
  theme_minimal() + 
  theme(panel.grid.major.y = element_blank(),
        panel.grid.minor.y = element_blank(),
        plot.title = element_text(face = "bold"))

# Cross-tabulation with cities
q12_cross_tab_city <- svytable(~q12 + city_mapped, design = design)

ggplot(as.data.frame(q12_cross_tab_city), aes(x = city_mapped, y = Freq, fill = q12)) +
  geom_bar(stat = "identity", position = "stack") +
  coord_flip() +
  scale_fill_manual(values = c("#041e42","#6eaddc","#da291c","#1B786E"),
                    limits = c("Strongly agree", "Agree", "Disagree", "Strongly disagree")) + 
  labs(title = "Majority agree that they learned new skills to manage developing 
a digital product, but some disagree in Macon and Detroit.",
       subtitle = paste("Rating Scale: 4 - Strongly Agree to 1 - Strongly Disagree (n =", total_sample, ")"),
       x = "",
       y = "Number of Responses",
       caption = "Source: TOPC Cohort 3 Survey (2023)") +
  theme_minimal() +
  theme(legend.position = "bottom",
        legend.box = "vertical",
        legend.box.margin = margin(0, 0, 0, 0),
        legend.title = element_blank(),
        panel.grid.major.y = element_blank(),
        panel.grid.minor.y = element_blank(),
        plot.title = element_text(face = "bold"),
        plot.caption = element_text(hjust = 0)) +
  guides(fill = guide_legend(nrow = 1, byrow = TRUE))
```

**Q13. I learned new skills for creating a product sustainability plan to ensure that product is improved and maintained.**

```{r}
#| label: q13
#| message: false

# Single-variable frequency plot
q13_frequency <- svytable(~q13, design = design)

ggplot(as.data.frame(q13_frequency), aes(x = q13, y = Freq)) +
  geom_bar(stat = "identity", fill = "#041e42", width = 0.7) +
  coord_flip() +
  labs(title = "Most respondents agree they learned new skills to create a
product sustainability plan.",
       subtitle = paste("Rating Scale: 4 - Strongly Agree to 1 - Strongly Disagree (n =", total_sample, ")"),
       x = "",
       y = "Number of Responses") +
  theme_minimal() + 
  theme(panel.grid.major.y = element_blank(),
        panel.grid.minor.y = element_blank(),
        plot.title = element_text(face = "bold"))

# Cross-tabulation with cities
q13_cross_tab_city <- svytable(~q13 + city_mapped, design = design)

ggplot(as.data.frame(q13_cross_tab_city), aes(x = city_mapped, y = Freq, fill = q13)) +
  geom_bar(stat = "identity", position = "stack") +
  coord_flip() +
  scale_fill_manual(values = c("#041e42","#6eaddc","#da291c","#1B786E"),
                    limits = c("Strongly agree", "Agree", "Disagree", "Strongly disagree")) + 
  labs(title = "Majority agree that they learned new skills to create a product 
sustainability plan, but some disagree in Detroit.",
       subtitle = paste("Rating Scale: 4 - Strongly Agree to 1 - Strongly Disagree (n =", total_sample, ")"),
       x = "",
       y = "Number of Responses",
       caption = "Source: TOPC Cohort 3 Survey (2023)") +
  theme_minimal() +
  theme(legend.position = "bottom",
        legend.box = "vertical",
        legend.box.margin = margin(0, 0, 0, 0),
        legend.title = element_blank(),
        panel.grid.major.y = element_blank(),
        panel.grid.minor.y = element_blank(),
        plot.title = element_text(face = "bold"),
        plot.caption = element_text(hjust = 0)) +
  guides(fill = guide_legend(nrow = 1, byrow = TRUE))
```

## Goal 2: Participant Confidence and Competence

**Q14. I have the skills and support to be able to innovate in my day-to-day work.**

```{r}
#| label: q14
#| message: false

# Single-variable frequency plot
q14_frequency <- svytable(~q14, design = design)

ggplot(as.data.frame(q14_frequency), aes(x = q14, y = Freq)) +
  geom_bar(stat = "identity", fill = "#041e42", width = 0.7) +
  coord_flip() +
  labs(title = "Most respondents agree they have the skills and support
to innovate in their everyday work.",
       subtitle = paste("Rating Scale: 4 - Strongly Agree to 1 - Strongly Disagree (n =", total_sample, ")"),
       x = "",
       y = "Number of Responses") +
  theme_minimal() + 
  theme(panel.grid.major.y = element_blank(),
        panel.grid.minor.y = element_blank(),
        plot.title = element_text(face = "bold"))

# Cross-tabulation with cities
q14_cross_tab_city <- svytable(~q14 + city_mapped, design = design)

ggplot(as.data.frame(q14_cross_tab_city), aes(x = city_mapped, y = Freq, fill = q14)) +
  geom_bar(stat = "identity", position = "stack") +
  coord_flip() +
  scale_fill_manual(values = c("#041e42","#6eaddc","#da291c","#1B786E"),
                    limits = c("Strongly agree", "Agree", "Disagree", "Strongly disagree")) + 
  labs(title = "Majority agree that they have the skills and support to innovate
in their everyday work, but some disagree in Detroit.",
       subtitle = paste("Rating Scale: 4 - Strongly Agree to 1 - Strongly Disagree (n =", total_sample, ")"),
       x = "",
       y = "Number of Responses",
       caption = "Source: TOPC Cohort 3 Survey (2023)") +
  theme_minimal() +
  theme(legend.position = "bottom",
        legend.box = "vertical",
        legend.box.margin = margin(0, 0, 0, 0),
        legend.title = element_blank(),
        panel.grid.major.y = element_blank(),
        panel.grid.minor.y = element_blank(),
        plot.title = element_text(face = "bold"),
        plot.caption = element_text(hjust = 0)) +
  guides(fill = guide_legend(nrow = 1, byrow = TRUE))
```

**Q17. I feel confident working with technical partners to design a tool and advance the tool's development.**

```{r}
#| label: q17
#| message: false

# Single-variable frequency plot
q17_frequency <- svytable(~q17, design = design)

ggplot(as.data.frame(q17_frequency), aes(x = q17, y = Freq)) +
  geom_bar(stat = "identity", fill = "#041e42", width = 0.7) +
  coord_flip() +
  labs(title = "Most respondents agree they feel confident working with technical
partners to design a tool.",
       subtitle = paste("Rating Scale: 4 - Strongly Agree to 1 - Strongly Disagree (n =", total_sample, ")"),
       x = "",
       y = "Number of Responses") +
  theme_minimal() + 
  theme(panel.grid.major.y = element_blank(),
        panel.grid.minor.y = element_blank(),
        plot.title = element_text(face = "bold"))

# Cross-tabulation with cities
q17_cross_tab_city <- svytable(~q17 + city_mapped, design = design)

ggplot(as.data.frame(q17_cross_tab_city), aes(x = city_mapped, y = Freq, fill = q17)) +
  geom_bar(stat = "identity", position = "stack") +
  coord_flip() +
  scale_fill_manual(values = c("#041e42","#6eaddc","#da291c","#1B786E"),
                    limits = c("Strongly agree", "Agree", "Disagree", "Strongly disagree")) + 
  labs(title = "Majority agree that they feel confident working with technical
partners, but some disagree in Detroit.",
       subtitle = paste("Rating Scale: 4 - Strongly Agree to 1 - Strongly Disagree (n =", total_sample, ")"),
       x = "",
       y = "Number of Responses",
       caption = "Source: TOPC Cohort 3 Survey (2023)") +
  theme_minimal() +
  theme(legend.position = "bottom",
        legend.box = "vertical",
        legend.box.margin = margin(0, 0, 0, 0),
        legend.title = element_blank(),
        panel.grid.major.y = element_blank(),
        panel.grid.minor.y = element_blank(),
        plot.title = element_text(face = "bold"),
        plot.caption = element_text(hjust = 0)) +
  guides(fill = guide_legend(nrow = 1, byrow = TRUE))
```

## Goal 3: Participant Recognition and Application of Methods

**Q20. I am applying the skills I'm learning in this program to my day-to-day work.**

```{r}
#| label: q20
#| message: false

# Single-variable frequency plot
q20_frequency <- svytable(~q20, design = design)

ggplot(as.data.frame(q20_frequency), aes(x = q20, y = Freq)) +
  geom_bar(stat = "identity", fill = "#041e42", width = 0.7) +
  coord_flip() +
  labs(title = "Most respondents agree they are applying the skills they have 
learned from the program in their everyday work.",
       subtitle = paste("Rating Scale: 4 - Strongly Agree to 1 - Strongly Disagree (n =", total_sample, ")"),
       x = "",
       y = "Number of Responses") +
  theme_minimal() + 
  theme(panel.grid.major.y = element_blank(),
        panel.grid.minor.y = element_blank(),
        plot.title = element_text(face = "bold"))

# Cross-tabulation with cities
q20_cross_tab_city <- svytable(~q20 + city_mapped, design = design)

ggplot(as.data.frame(q20_cross_tab_city), aes(x = city_mapped, y = Freq, fill = q20)) +
  geom_bar(stat = "identity", position = "stack") +
  coord_flip() +
  scale_fill_manual(values = c("#041e42","#6eaddc","#da291c","#1B786E"),
                    limits = c("Strongly agree", "Agree", "Disagree", "Strongly disagree")) + 
  labs(title = "Majority agree that they apply the skills they have learned from the 
program, with Miami strongly agreeing the most.",
       subtitle = paste("Rating Scale: 4 - Strongly Agree to 1 - Strongly Disagree (n =", total_sample, ")"),
       x = "",
       y = "Number of Responses",
       caption = "Source: TOPC Cohort 3 Survey (2023)") +
  theme_minimal() +
  theme(legend.position = "bottom",
        legend.box = "vertical",
        legend.box.margin = margin(0, 0, 0, 0),
        legend.title = element_blank(),
        panel.grid.major.y = element_blank(),
        panel.grid.minor.y = element_blank(),
        plot.title = element_text(face = "bold"),
        plot.caption = element_text(hjust = 0)) +
  guides(fill = guide_legend(nrow = 1, byrow = TRUE))
```

**Q7. My team has defined a role for residents or the community in designing services moving forward.**

```{r}
#| label: q7
#| message: false

# Single-variable frequency plot
q7_frequency <- svytable(~q7, design = design)

ggplot(as.data.frame(q7_frequency), aes(x = q7, y = Freq)) +
  geom_bar(stat = "identity", fill = "#041e42", width = 0.7) +
  coord_flip() +
  labs(title = "Most respondents agree their teams have defined a role for the 
community to design services moving forward.",
       subtitle = paste("Rating Scale: 4 - Strongly Agree to 1 - Strongly Disagree (n =", total_sample, ")"),
       x = "",
       y = "Number of Responses") +
  theme_minimal() + 
  theme(panel.grid.major.y = element_blank(),
        panel.grid.minor.y = element_blank(),
        plot.title = element_text(face = "bold"))

# Cross-tabulation with cities
q7_cross_tab_city <- svytable(~q7 + city_mapped, design = design)

ggplot(as.data.frame(q7_cross_tab_city), aes(x = city_mapped, y = Freq, fill = q7)) +
  geom_bar(stat = "identity", position = "stack") +
  coord_flip() +
  scale_fill_manual(values = c("#041e42","#6eaddc","#da291c","#1B786E"),
                    limits = c("Strongly agree", "Agree", "Disagree", "Strongly disagree")) + 
  labs(title = "Majority agree their teams have defined a role for the community to 
design services moving forward, with Miami and Macon strongly 
agreeing the most.",
       subtitle = paste("Rating Scale: 4 - Strongly Agree to 1 - Strongly Disagree (n =", total_sample, ")"),
       x = "",
       y = "Number of Responses",
       caption = "Source: TOPC Cohort 3 Survey (2023)") +
  theme_minimal() +
  theme(legend.position = "bottom",
        legend.box = "vertical",
        legend.box.margin = margin(0, 0, 0, 0),
        legend.title = element_blank(),
        panel.grid.major.y = element_blank(),
        panel.grid.minor.y = element_blank(),
        plot.title = element_text(face = "bold"),
        plot.caption = element_text(hjust = 0)) +
  guides(fill = guide_legend(nrow = 1, byrow = TRUE))
```

## Goal 4: Participant Satisfaction and Intention to Action

**Q21. I would recommend this program to my peers.**

```{r}
#| label: q21
#| message: false

# Single-variable frequency plot
q21_frequency <- svytable(~q21, design = design)

all_levels_df <- data.frame(q21 = factor(1:4, levels = 1:4), Freq = numeric(4))

q21_frequency_df <- merge(all_levels_df, as.data.frame(q21_frequency), by = "q21", all.x = TRUE)
q21_frequency_df$Freq <- rowSums(q21_frequency_df[, c("Freq.x", "Freq.y")], na.rm = TRUE)

q21_post_frequency_plot <- ggplot(q21_frequency_df, aes(x = q21, y = Freq)) +
  geom_bar(stat = "identity", fill = "#041e42", width = 0.7) +
  coord_flip() +
  labs(title = "All respondents agree they would recommend this program 
to their peers.",
       subtitle = paste("Rating Scale: 4 - Strongly Agree to 1 - Strongly Disagree (n =", total_sample, ")"),
       x = "",
       y = "Number of Responses") +
  theme_minimal() + 
  theme(panel.grid.major.y = element_blank(),
        panel.grid.minor.y = element_blank(),
        plot.title = element_text(face = "bold"),
        plot.caption = element_text(hjust = 0))

print(q21_post_frequency_plot)

ggsave("q21_post_frequency_plot.png", q21_post_frequency_plot)

# Cross-tabulation with cities
q21_cross_tab_city <- svytable(~q21 + city_mapped, design = design)

ggplot(as.data.frame(q21_cross_tab_city), aes(x = city_mapped, y = Freq, fill = q21)) +
  geom_bar(stat = "identity", position = "stack") +
  coord_flip() +
  scale_fill_manual(values = c("#041e42","#6eaddc","#da291c","#1B786E"),
                    limits = c("Strongly agree", "Agree", "Disagree", "Strongly disagree")) + 
  labs(title = "Majority agree they would recommend this program to their peers, 
with Miami and Akron strongly agreeing the most.",
       subtitle = paste("Rating Scale: 4 - Strongly Agree to 1 - Strongly Disagree (n =", total_sample, ")"),
       x = "",
       y = "Number of Responses",
       caption = "Source: TOPC Cohort 3 Survey (2023)") +
  theme_minimal() +
  theme(legend.position = "bottom",
        legend.box = "vertical",
        legend.box.margin = margin(0, 0, 0, 0),
        legend.title = element_blank(),
        panel.grid.major.y = element_blank(),
        panel.grid.minor.y = element_blank(),
        plot.title = element_text(face = "bold"),
        plot.caption = element_text(hjust = 0)) +
  guides(fill = guide_legend(nrow = 1, byrow = TRUE))
```
